### 2019-12-31 overview.tex
NYE

The preceding section presents the most basic solutions of the Stokes equation in the presence of only one particle.
In practice, however, it is rarely the case particles or droplets exist in isolation.
Particles tend to abound; and they often interact with each other through various types of hydrodynamic or non-hydrodynamic mechanisms, giving rise to a multitude of phenomena in natural or artificial conditions.
For example, soap bubbles are always in a cluster due to the interfacial capillary attraction, while the same underlying principle can be applied to manipulate droplet motions on a surface to aid liquid handling \citep{vapour-sensing}.
To offer at least some partial insights on the hydrodynamics, we highlight recent theoretical development of droplet interactions in bulk microflows, starting from the simplest case of two particles immersed in unbounded simple shear flows.

@@

Among the early studies of suspension hydrodynamics, \cite{batchelor_green_1972} solved completely the dynamics of two rigid spheres of arbitrary sizes subject to a background fluid motion whose velocity at infinity is a linear function of position, \ie
${\bm u}^\infty \sim {\bm E}^\infty \cdot {\bm x} + {\bm \omega}^\infty \times {\bm x}$ as $\abs{{\bm x}} \to \infty$.
The solution entails the relative velocity of the two sphere centers and their force dipole strengths (related to the effective viscosity of the suspension, see Section \ref{sec:sus-rheo}), and is given in terms of several geometric parameters functions of the spheres' relative position and size ratio.
In the special case of two equal-sized spheres suspended in simple shear flows, the relative velocity can be integrated numerically to yield a trajectory diagram as in Figure \ref{fig:BG-traj}.
Here, two types of trajectories can be observed:
(i) an \emph{open} trajectory where one particle approaches the other particle from one side, overtakes it, and continues in the same direction to infinity; and
(ii) a \emph{closed} trajectory where two particles stay bound and rotate around each other permanently regardless of how far they may separate temporarily.
It was noted by the authors that, under such ideal conditions (\eg smooth particle surface), the separatrix between open and closed trajectories encloses an infinite volume.
Furthermore, if the two particles are once aligned in the flow direction, they will form a closed loop forever.
% or we can call this a naive man's projection of his relationship ;)

@@

We note that, in both cases, the relative particle velocity is proportional to the shear rate of the underlying flow.
That is, doubling the shear will result in twice as fast relative motion between the particles, though the relative velocity remains much smaller than the absolute velocity in the lab frame (typically two orders-of-magnitude smaller).
Hence, these are truly slow, but long-range, interactions.
In the case of liquid droplets, an additional constraint needs to be satisfied for the above analysis to hold, \ie Ca $\ll 1$.
This is usually the case for microfluidic applications.
Following the same example as considered in Section \ref{sec:stokes-flows}, and suppose it is an oil droplet traveling in water (the surface tension coefficient would be around 0.05 N/m, depending on surfactants and the temperature) under a relatively large shear rate of $10^3$ s$^{-1}$, then Ca $\sim 10^{-4}$, which is small enough for the droplet to remain spherical in the flow.

@@

With a distant wall, we show possibility of a stationary position.
Also dancing and swapping (\emph{Paper 4}). figure.
Here the wall can be considered as the third particle.
note the fact that the rate is very slow, since the relative velocity is small.

\begin{figure}%[t]
  \centering
  \includegraphics[width=\columnwidth]{itzhak-boris.pdf}
  \caption{Trajectory map of two equal spheres in ...}
  \label{fig:itzhak-boris}
\end{figure}

With two walls, \cite{zurita-gotor_2007}
swapping.

>>>>

The preceding section presents the most basic solutions of the Stokes equation in the presence of only one particle.
In practice, however, it is rarely the case particles or droplets exist in isolation.
Particles tend to abound; and they often interact with each other through various types of hydrodynamic or non-hydrodynamic mechanisms, giving rise to a multitude of phenomena in natural or artificial conditions.
For example, soap bubbles are always in a cluster due to the interfacial capillary attraction, while the same underlying principle can be applied to manipulate droplet motions on a surface to aid liquid handling \citep{vapour-sensing}.
To offer at least some partial insights on the hydrodynamics, we highlight recent theoretical developments of droplet interactions in bulk microflows, starting from the simplest case of two particles immersed in unbounded simple shear flows.

@@

Among the early studies of suspension hydrodynamics, \cite{batchelor_green_1972} solved completely the dynamics of two rigid spheres of arbitrary sizes subject to a background fluid motion whose velocity at infinity is a linear function of position, \ie
${\bm u}^\infty \sim {\bm E}^\infty \cdot {\bm x} + {\bm \omega}^\infty \times {\bm x}$ as $\abs{{\bm x}} \to \infty$.
The solution entails the relative velocity of the two sphere centers and their force dipole strengths (related to the effective viscosity of the suspension, see Section \ref{sec:sus-rheo}), and is given in terms of several geometric parameters functions of the spheres' relative position and size ratio.
In the special case of two equal-sized spheres suspended in simple shear flows, the relative velocity can be integrated numerically to yield a phase diagram as in Figure \ref{fig:BG-traj}.
Here, two types of trajectories can be observed:
(i) an \emph{open} trajectory where one particle approaches the other particle from one side, overtakes it, and continues in the same direction to infinity; and
(ii) a \emph{closed} trajectory where two particles stay bound and rotate around each other permanently regardless of how far they may separate temporarily.
It was noted by the authors that, under such ideal conditions (\eg smooth particle surface), the separatrix between open and closed trajectories encloses an infinite volume.
Furthermore, if the two particles are once aligned in the flow direction, they will form a closed loop forever.
% or we can call this a naive man's projection of his relationship ;)

@@

We note that, in both cases, the relative particle velocity is proportional to the shear rate of the underlying flow.
That is, doubling the shear will result in twice as fast relative motion between the particles, though the relative velocity remains much smaller than the absolute velocity in the lab frame (typically two orders-of-magnitude smaller).
Hence, these are truly slow, but long-range, interactions.
In the case of liquid droplets, an additional constraint needs to be satisfied for the above analysis to hold, \ie Ca $\ll 1$.
This is usually the case for microfluidic applications.
For example, recall the example as considered in the beginning of Section \ref{sec:stokes-flows}, and suppose it is an oil droplet traveling in water (the surface tension coefficient would be around 0.05 N/m, depending on surfactants and the temperature) under a relatively large local shear rate of $\dot{\gamma}=10^3$ s$^{-1}$, then the capillary number Ca $=\mu(a\dot{\gamma})/\gamma \sim 10^{-4}$, which is small enough for the droplet to remain spherical in the flow.

@@

\begin{figure}%[t]
  \centering
  \includegraphics[width=\columnwidth]{itzhak-boris.pdf}
  \caption{
  (left) Trajectory map of two equal spheres in simple shear flows bounded by a distant wall. The distance between the reference particle (located at the origin) and the wall is $z_0=5a$, where $a$ is the particle radius. $r_s$ and $r_c$ denote the saddle point and the neutral equilibrium point, respectively.
  (right) Schematic illustrations of the stationary configuration (upper) and the dancing trajectory (lower).}
  \label{fig:itzhak-boris}
\end{figure}

When walls are present, particles not only interact with each other but also indirectly interact with the wall, or equivalently, interact with their reflection images such that the boundary conditions along the wall are satisfied \citep{blake_1971, LironMochon}.
Consequently, pair interactions in bounded flows may differ at least quantitatively from the unbouned conditions.

We first consider the simplest modification -- the inclusion of one wall.
Using an boundary integral representation (\emph{Paper 3}), we recently solved the relative velocity of two rigid particles in simple shear flows above a distant wall (\emph{Paper 4}).
The results are illustrated in Figure \ref{fig:itzhak-boris}.
Here, the blue curves denote the closed trajectories, and the red curves denote the open ones.
First, we see there are two disconnected closed regions; one being a degenerate of the BG trajectory, the other indicating rotation around a center (which we call ``dancing'' trajectories).
The latter suggest the existence a stationary position.
Note that the trajectories are axisymmetric. Thus, particles can travel together without relative motions in a whole range of configurations.
The intersection between the blue and red curves represents the unstable saddle point.
Furthermore, the red curves indicates previously identified ``swapping trajectories'' \citep{zurita-gotor_2007}.
Overall, the phase portrait of two particles in wall-bounded shear flows is topologically different from BG.

\begin{figure}%[t]
  \centering
  \includegraphics[width=0.55\columnwidth]{stresslet_reflection.png}
  \caption{Swapping mechanism.}
  \label{fig:stresslet-refl}
\end{figure}

Some mentioning of the swapping mechanism.
With two walls, \cite{zurita-gotor_2007}

also talk about my particle array.
crossover from trapping to passing.

### 2019-12-31 paper5/article.tex
NYE

Besides the parameters just defined and based on the geometrical dimensions and initial and boundary conditions alone, in the following discussion we will use other nondimensional numbers because they turned out to be more relevant to understand the problem at hand; in particular, the two non-dimensional parameters which characterize the single-phase homogeneous shear turbulent flows, the Taylor-microscale Reynolds number $Re_\lambda$ and the shear-rate parameter $S^*$, defined as
\begin{equation}
\label{eq:rel}
Re_\lambda = \left( \frac{2\mathcal{K} }{3} \right)^{1/2} \frac{\lambda}{\nu} = \left( \frac{5}{3 \nu \varepsilon } \right)^{1/2} 2\mathcal{K},
\end{equation}
and
\begin{equation}
\label{eq:ss}
S^* = \frac{2 \mathcal{S} \mathcal{K} }{\varepsilon},
\end{equation}
where $\lambda = \sqrt{10\nu \mathcal{K}/\varepsilon}$ is the Taylor microscale \citep{sekimoto_dong_jimenez_2016a}, $\mathcal{K} = \langle \rho u'_i u'_i \rangle/2$ is the turbulent kinetic energy per unit volume, and $\varepsilon = \mu \langle \partial u'_i/\partial x_j \partial u'_i/\partial x_j \rangle$ is the dissipation rate of the fluctuating energy. These two non-dimensional numbers can be interpreted as the ratio of the eddy-turnover time $\tau_0= \left( 2\mathcal{K} \right)^{1/2}/\varepsilon$ and the Kolmogorov time scale $\tau_K= \left( \nu / \varepsilon \right)^{1/2}$ and the mean shear time scale $\tau_\mathcal{S} = 1/ \mathcal{S}$, respectively.

@@

\figrefC[a]{fig:count} shows the temporal evolution of the number of droplets ($\mathcal{N}$) under various $We_\lambda$ and initial sizes $D_0$. The counting of the droplets is conducted automatically by checking the connectivity of the local VOF field ($\phi$) using a $n$-dimensional image processing library\footnote{scipy.ndimage, https://docs.scipy.org/doc/scipy/reference/ndimage.html}. We observe that $\mathcal{N}$ has an initial transient phase of same duration as the fluid transient phase observed previously in \figref[a]{fig:kin} ($t\mathcal{S} \lesssim 50$), before the droplets count approaches a statistically steady value for all the cases considered, consistently with the statistically stationarity of the averaged global flow quantities. Note that, the final state is a statistically steady state since the number of droplets $\mathcal{N}$ is not constant but continuously varies and oscillates around a mean value, denoted later on as $\mathcal{N}_s$. From the figure we observe also that the initial transient phase differs among the cases, with three distinct behaviors evident: \textit{i)} in most of the cases, $\mathcal{N}$ increases rapidly after the injection (within $t \mathcal{S} \approx 10$); however, the growth slows down and $\mathcal{N}$ reaches its final steady state value almost monotonically; \textit{ii)} cases $4$ and $5$ exhibit a significant overshoot of the number of droplets $\mathcal{N}$ for short times before $\mathcal{N}$ reduces to the final regime values due to the coalescence; \textit{iii)} case $3$ shows an initial decrease of the number of droplets followed by an increase. Notwithstanding the different behaviors, in all the cases the final number of droplets is always larger than the initial one.

>>>>

Besides the parameters just defined and based on the geometrical dimensions and initial and boundary conditions alone, in the following discussion we will use other nondimensional numbers because they turned out to be more relevant to understand the problem at hand; in particular, the two non-dimensional parameters which characterize the single-phase homogeneous shear turbulent flows, the Taylor-microscale Reynolds number $Re_\lambda$ and the shear-rate parameter $S^*$, defined as
\begin{equation}
\label{eq:rel}
Re_\lambda = \left( \frac{2\mathcal{K} }{3} \right)^{1/2} \frac{\lambda}{\nu} = \left( \frac{5}{3 \nu \varepsilon } \right)^{1/2} 2\mathcal{K},
\end{equation}
and
\begin{equation}
\label{eq:ss}
S^* = \frac{2 \mathcal{S} \mathcal{K} }{\varepsilon},
\end{equation}
where $\lambda = \sqrt{10\nu \mathcal{K}/\varepsilon}$ is the Taylor microscale \citep{sekimoto_dong_jimenez_2016a}, $\mathcal{K} = \langle \rho u'_i u'_i \rangle/2$ is the turbulent kinetic energy per unit volume, and $\varepsilon = \mu \langle \partial u'_i/\partial x_j : \partial u'_i/\partial x_j \rangle$ is the dissipation rate of the fluctuating energy. These two non-dimensional numbers can be interpreted as the ratio of the eddy-turnover time $\tau_0= \left( 2\mathcal{K} \right)^{1/2}/\varepsilon$ and the Kolmogorov time scale $\tau_K= \left( \nu / \varepsilon \right)^{1/2}$ and the mean shear time scale $\tau_\mathcal{S} = 1/ \mathcal{S}$, respectively.

@@

\figrefC[a]{fig:count} shows the temporal evolution of the number of droplets ($\mathcal{N}$) under various $We_\lambda$ and initial sizes $D_0$. The counting of the droplets is conducted automatically by checking the connectivity of the local VOF field ($\phi$) using a $n$-dimensional image processing library\footnote{Scipy.ndimage, \texttt{https://docs.scipy.org/doc/scipy/reference/ndimage.html}.}. We observe that $\mathcal{N}$ has an initial transient phase of same duration as the fluid transient phase observed previously in \figref[a]{fig:kin} ($t\mathcal{S} \lesssim 50$), before the droplets count approaches a statistically steady value for all the cases considered, consistently with the statistically stationarity of the averaged global flow quantities. Note that, the final state is a statistically steady state since the number of droplets $\mathcal{N}$ is not constant but continuously varies and oscillates around a mean value, denoted later on as $\mathcal{N}_s$. From the figure we observe also that the initial transient phase differs among the cases, with three distinct behaviors evident: \textit{i)} in most of the cases, $\mathcal{N}$ increases rapidly after the injection (within $t \mathcal{S} \approx 10$); however, the growth slows down and $\mathcal{N}$ reaches its final steady state value almost monotonically; \textit{ii)} cases $4$ and $5$ exhibit a significant overshoot of the number of droplets $\mathcal{N}$ for short times before $\mathcal{N}$ reduces to the final regime values due to the coalescence; \textit{iii)} case $3$ shows an initial decrease of the number of droplets followed by an increase. Notwithstanding the different behaviors, in all the cases the final number of droplets is always larger than the initial one.
